Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-25 report/report.tex
Update todo
Add percentages to building matching statistics table
Update SLU building accuracy
Update data from collision run

The SLU map contains building features and property limits, but no road data.
The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The SLU data is aqqcuired by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Property limits and building features have a position accuracy requirement of 5 meters.
(Lantmäteriet, 2019)

@@

% TUESDAY
% TODO: ANALYSIS SECTION, figure out what to write

% TODO: Collision correction: Fix collisions by relaxing both feature_1 and feature_2
% TODO: Collision correction: Edit edge distance function to factor in width of the other path

% WEDNESDAY
% TODO: Collision correction run
% TODO: Figure of street, before correction, after correction
% TODO: Table for collision correction data in report

% TODO: Write analysis section
% TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?

% THURSDAY
% TODO: Proof read entire report
% TODO: Start large data run, way collision

@@

@@

\begin{table}[H]
\begin{tabular}{lllll}
    & 1:0 & 1:1 & 1:n & Total \\
    Match count & 9812 & 81722 & 11221 & 102755
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 1391          & 256          & 107         & 148         \\
    Nodes, total            & 264179        & 26771        & 6997        & 10686       \\
    Edge length, total      & 5004997.34 m  & 814349.47 m  & 169129.19 m & 307461.81 m \\
    Features, colliding     & 186           & 65           & 20          & 29          \\
    Nodes, colliding        & 458           & 239          & 45          & 59          \\
    Edge length, colliding  & 14445.66 m    & 8887.32 m    & 1467.54 m   & 1930.88 m   \\
    Features, percent       & 13.37 \%      & 25.39 \%     & 18.69 \%    & 19.59 \%    \\
    Nodes, percent          & 0.17 \%       & 0.89 \%      & 0.64 \%     & 0.55 \%     \\
    Edge length, percent    & 0.29 \%       & 1.09 \%      & 0.87 \%     & 0.63 \%

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & & & & \\
    Nodes, total            & & & & \\
    Edge length, total      & m & m & m & m \\
    Features, colliding     & & & & \\
    Nodes, colliding        & & & & \\
    Edge length, colliding  & m & m & m & m \\
    Features, percent       & \% & \% & \% & \% \\
    Nodes, percent          & \% & \% & \% & \% \\
    Edge length, percent    & \% & \% & \% & \%

@@

TODO: Interview with Todor

>>>>

The SLU map contains building features and property limits, but no road data.
The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The SLU data is aqqcuired by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Building features have a position accuracy requirement of 2 meters.
(Lantmäteriet, 2019)

@@

% TODO: Collision correction run (Enter data in report)
% TODO: Figure of street, before correction, after correction

% LARGE DATA RUN
% TODO: Start large data run, way collision
% TODO: Enter for correction data in report

@@

% TODO: Write disposition for implementation of the collision checker

@@

\begin{table}[H]
\begin{tabular}{lllll}
    & 1:0 & 1:1 & 1:n & Total \\
    Match count & 9812   & 81722   & 11221   & 102755 \\
    Percent     & 9.55\% & 79.53\% & 10.92\% & 100\%
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 1391          & 256          & 107         & 148         \\
    Nodes, total            & 264179        & 26771        & 6997        & 10686       \\
    Edge length, total      & 5004997.34 m  & 814349.47 m  & 169129.19 m & 307461.81 m \\
    Features, colliding     & 141           & 24           & 20          & 22          \\
    Nodes, colliding        & 302           & 48           & 38          & 42          \\
    Edge length, colliding  & 7779.66 m     & 1197.50 m    & 1074.88 m   & 1291.26 m   \\
    Features, percent       & 10.13 \%      & 9.38 \%      & 18.69 \%    & 14.86 \%    \\
    Nodes, percent          & 0.11 \%       & 0.18 \%      & 0.54 \%     & 0.39 \%     \\
    Edge length, percent    & 0.015 \%      & 0.15 \%      & 0.64 \%     & 0.42 \%

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, colliding     & 1             & 0            & 2           & 0           \\
    Nodes, colliding        & 1             & 0            & 2           & 0           \\
    Edge length, colliding  & 4.20 m        & 0.00 m       & 17.67 m     & 0.00 m      \\
    Features, percent       & 0.07 \%       & 0.00 \%      & 1.87 \%     & 0.00 \%     \\
    Nodes, percent          & 0.00 \%       & 0.00 \%      & 0.02 \%     & 0.00 \%     \\
    Edge length, percent    & 0.00 \%       & 0.00 \%      & 0.01 \%     & 0.00 \%

@@

% TODO: Interview with Todor
